dispRity demo for ecological data

### 2015-10-09 doc/dispRity-ecology-demo.Rnw

<<installation, eval=FALSE>>=
install.packages("devtools")
library(devtools)
install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)
@

Note that we use the \texttt{master} branch here which is version \Sexpr{packageVersion("dispRity")}.
This is the piping-hot latest version.
If you want a more stable (and tested version), change \texttt{ref = "master"} to \texttt{ref = "release"}.
This package depends mainly on the \texttt{ape} package and the \texttt{timeSliceTree::paleotree} function.

>>>>

<<installation, eval=FALSE>>=
install.packages("devtools")
library(devtools)
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)
@

Note that we use the \texttt{release} branch here which is version 0.1.1.
If you want the piping-hot (and full of bugs) version, change the option \texttt{ref = "release"} to \texttt{ref = "master"}.
This package depends mainly on the \texttt{ape} package and the \texttt{timeSliceTree::paleotree} function.
